Optimal Light Curve Attitude Inversion with Measurement Noise: Two Case Studies

### 2025-03-10 paper.tex
almost done kinda

% \bibliographystyle{alpha}
\bibliographystyle{plain}

% \usepackage[style=apa, natbib=true]{biblatex} % Use 'apa' style instead of 'apalike'
\usepackage{url} % Ensure URLs are properly formatted
% \addbibresource{cache/refs.bib} % Use biblatex's method for loading the bibliography

\usepackage{times}
\usepackage[numbers]{natbib}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{bm} % for bold math
\usepackage{mathtools} % for \prescript
\newcommand{\vctr}[1]{\bm{#1}}
\newcommand{\unitv}[1]{\hat{\vctr{#1}}}
\newcommand{\preup}[1]{\prescript{#1}{}{}}
\newcommand{\rf}[1]{\mathcal{\MakeUppercase{#1}}}
\newcommand{\dcm}[1]{\left[\rf{#1}\right]}
\newcommand{\vrf}[2]{\preup{\rf{#1}}\vctr{#2}}
\newcommand{\mbar}[0]{\;\middle|\;}
\newcommand{\prf}[1]{\preup{\rf{#1}}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\DeclareMathOperator{\atantwo}{atan2}
\DeclareMathOperator{\fl}{floor}

@@

\FloatBarrier
\section{Inversion Method}

@@

\begin{equation} \label{eq:nll_loss}
 f(\hat{\vctr{S}}, \vctr{S}) = \frac{1}{m}\sum_{k=1}^{m}\left[\ln\sigma_k + \frac{1}{2}\left(\frac{S_k - \hat{S}_k}{\sigma_k}\right)^2 \right].
 \end{equation}

In this work, the light curve and its standard deviation are always assumed to be expressed in a linear unit, e.g., analog-to-digital units (ADU) or irradiance proportional to $W/m^2$.

\subsection{State Vector Definition and Dynamics}

@@

\FloatBarrier
\section{Computing the Light Curve}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figmed]{obs_geom.png}
  \caption{Facet geometry including the observer direction $\unitv{o}$, Sun direction $\unitv{s}$, normal vector $\unitv{n}_i$, unshadowed area $\bar{a}_i$, shadowed area $\tilde{a}_i$, and counterclockwise vertex positions $\left\{ \vctr{v}_{i,1}, \vctr{v}_{i,2}, \vctr{v}_{i,3} \right\}$.}
  \label{fig:facet_geom}
\end{figure}

@@

[\textit{TODO: describe the variables here, if we want to keep this eq... it's in the cited paper so I am not sure}]

@@

\begin{equation}
 S_{\text{SO},k} \sim \mathcal{N}\left( \bar{S}_{\text{SO},k}, \sigma^2_{S,k} \right).
 \end{equation}

\FloatBarrier
\section{Attitude Inversion Results for Synthetic Data}

To demonstrate the effectiveness of this method, we first present results for a simulated light curve where the ground truth is known.

\begin{table}[ht]
  \centering
  \caption{Simulated observation parameters}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Target COSPAR ID & 1990-054D \\ \hline
  First obs.\ (UTC) & Mar 8, 2025 02:00:00.000 \\ \hline
  Light curve duration & $5$ minutes \\ \hline
  Observations & $100$ \\ \hline
  Integration time & $0.5$ seconds \\ \hline
  \end{tabular}
  \label{tb:case1_in}
\end{table}

\begin{table}[ht]
  \centering
  \caption{Reflection properties of materials used in the synthetic data test case. The authors estimated the white paint parameters qualitatively}
  \vspace*{6pt}
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Material} & $C_d$ & $C_s$ & $n$ \\ \hline
  Aluminum \cite{fankhauser2023} & $0.34$ & $0.40$ & $8.9$ \\ \hline
  White paint & $0.9$ & $0.1$ & $1$ \\ \hline
  \end{tabular}
  \label{tb:real_matprops}
 \end{table}

\begin{table}[ht]
  \centering
  \caption{True object attitude profile for all test cases}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
 Initial orientation & $\vctr{p}(0) = -\frac{1}{3} \begin{bmatrix} 1 & 1 & 1 \end{bmatrix}^T$ \\ \hline
 Initial $\vctr{\omega}$ ($\text{rad}/\text{s}$) & $\vctr{\omega}(0) = \begin{bmatrix} 0.03 & 0.06 & 0.03 \end{bmatrix}^T$ \\ \hline
 Inertia tensor ratios & $J_y / J_x = 1, \: J_z / J_x = 0.25$ \\ \hline
 External torque & $\vctr{M}=\begin{bmatrix} 0 & 0 & 0 \end{bmatrix}^T$ \\ \hline
  \end{tabular}
  \label{tb:synth_truth}
\end{table}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{rocket_bodies2.png}
  \caption{Measured rocket body model \cite{nasa_models}.}
  \label{fig:meas_model}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{rocket_bodies1.png}
  \caption{Simplified rocket body model used for inversion.}
  \label{fig:inv_model}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{light_curves_adu_rocket_body.png}
  \caption{Simulated observed flux for the rocket body.}
  \label{fig:obs_adu_synth}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{light_curves_mag_rocket_body.png}
  \caption{Simulated observed V-band magnitude for the rocket body.}
  \label{fig:obs_mag_synth}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{light_curves_std_rocket_body.png}
  \caption{Simulated observed light curve standard deviation computed with Equation \ref{eq:sigma_total}.}
  \label{fig:obs_std_synth}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{sigma_solsRocket Body.png}
  \caption{Converged solution initial orientation MRP vectors.}
  \label{fig:omega_sols1}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{omega_sols_Rocket Body.png}
  \caption{Converged solution initial body-frame angular velocities.}
  \label{fig:omega_sols1}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{spin_proc_Rocket Body.png}
  \caption{Converged solution body-frame spin and precession rates.}
  \label{fig:omega_sols1}
\end{figure}

\FloatBarrier
\section{Attitude Inversion Results for Real Data}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figsmall]{star37e.JPG}
  \caption{Star-37E upper stage \cite{star37_af}.}
  \label{fig:star37e}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_models_002.png}
  \caption{Simplified Star-37E model used for inversion.}
  \label{fig:star37e_simple}
\end{figure}

@@

\begin{table}[ht]
  \centering
  \caption{Delta I rocket body observation parameters}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Target COSPAR ID & 1984-115C \\ \hline
  First obs.\ (UTC) & Mar 2, 2025 01:53:30.251 \\ \hline
  Light curve duration & $7.5$ minutes \\ \hline
  Observations & $100$ ($92$ extracted) \\ \hline
  Obs.\ frequency & $0.222$ Hz \\ \hline
  Integration time & $3$ seconds \\ \hline
  \end{tabular}
  \label{tb:case1_in}
\end{table}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_lcs_001_2_00x.png}
  \caption{Selected light curve for the Delta (Star-37E) rocket body, observed by the Purdue Optical Ground Station}
  \label{fig:rb_lc_obs}
\end{figure}

\begin{table}[ht]
  \centering
  \caption{Delta I rocket body inversion assumptions}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Uniform BRDF & $C_d=0.2$, $C_s=0.8$, $n=30$ \\ \hline
  $|\omega(0)|_\text{max}$ & $8.31$ $\text{deg} / \text{s}^{-1}$ \\ \hline
  \end{tabular}
  \label{tb:case1_ass}
\end{table}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figbig]{EchoStar-1_image.jpg}
  \caption{ECHOSTAR II artist's rendition \cite{as7000_astronautix}.}
  \label{fig:echostar1}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_models_001.png}
  \caption{Simplified ECHOSTAR II box-wing model used for inversion.}
  \label{fig:echostar1_simple}
\end{figure}

The contribution of the bus to the total inertia tensor of ECHOSTAR II is spherically symmetric and given by: [\textit{TODO: citation needed}]:

@@

\noindent
assuming that the center of mass (COM) of the bus coincides with the COM of the entire vehicle. By the intermediate axis theorem, the contribution of a panel to the inertia tensor is a function of the displacement of the panel's COM from the vehicle's overall COM $\vctr{r}_p = [ 0, s/2 - l_p/2, 0]^T$ [\textit{TODO: citation needed}]:

@@

\noindent
assuming that the panels have negligible thickness. The overall inertia tensor for ECHOSTAR II is:

@@

\begin{table}[ht]
  \centering
  \caption{ECHOSTAR II observation parameters}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Target COSPAR ID & 1996-055A \\ \hline
  First obs.\ (UTC) & Feb 26, 2025 04:16:12.279 \\ \hline
  Light curve duration & $19.5$ minutes \\ \hline
  Observations & $456$ ($395$ extracted) \\ \hline
  Obs.\ frequency & $0.388$ Hz \\ \hline
  Integration time & $1$ seconds \\ \hline
  \end{tabular}
  \label{tb:case2_in}
\end{table}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_lcs_002_2_00x.png}
  \caption{Selected light curve for ECHOSTAR II, observed by the Purdue Optical Ground Station}
  \label{fig:sat_lc_obs}
\end{figure}

We estimate a maximum bound for the angular velocity magnitude by inspecting the light curve [\textit{TODO: finish sentence}]

\begin{table}[ht]
  \centering
  \caption{ECHOSTAR II inversion assumptions}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Material} & \textbf{Coefficients} \\ \hline
  Aluminum BRDF & $C_d=0.22$, $C_s=0.4$, $n=5$ \\ \hline
  MLI BRDF & $C_d=0.05$, $C_s=0.24$, $n=20$ \\ \hline
  Solar panel BRDF & $C_d=0.05$, $C_s=0.13$, $n=10$ \\ \hline
  $|\omega(0)|_\text{max}$ & $2.32$ $\text{deg} / \text{s}^{-1}$ \\ \hline
  \end{tabular}
  \label{tb:case2_ass}
\end{table}

\FloatBarrier
\section*{Acknowledgments}

@@

\FloatBarrier
\section*{Appendix}

\begin{table}[ht]
  \centering
  \caption{Telescope information common to all test cases}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  CCD sensor & KAF-16803 \\ \hline
  Effective aperture area $A_\circ$ & $0.076$ $m^2$ \\ \hline
  Observer location & $32.900^\circ \textrm{ N}, -105.533^\circ \textrm{ W}$ \\ \hline
  Observer altitude & $2.24$ km above MSL \\ \hline
  Source pixels $n_\text{pix}$ & $100$ \\ \hline
  Read noise $\sigma_\text{read}$ & $9$ $\text{ADU} / \text{pixel}$ \\ \hline
  Dark current rate $\lambda_\text{dark}$ & $0.01$ $\text{ADU} / \text{pixel} / \text{s}$ \\ \hline
  Flat field strength $f_k$ & $0.01$ nondim \\ \hline
  Gain $g$ & $5.1$ $e^- / \text{ADU}$ \\ \hline
  \end{tabular}
  \label{tb:tele_info}
 \end{table}

 \begin{table}[ht]
  \centering
  \caption{BFGS solver configuration for all results cases}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Maximum function evaluations & $1000$ \\ \hline
  Maximum iterations & $100$ \\ \hline
  Finite difference step size & $1 \cdot 10^{-5}$ \\ \hline
  Gradient $\infty$-norm tolerance & $1 \cdot 10^{-5}$ \\ \hline
  \end{tabular}
  \label{tb:bfgs_info}
 \end{table}

\FloatBarrier
\clearpage
\bibliography{cache/refs.bib}
\end{document}

>>>>

\bibliographystyle{plain}

\usepackage{float}

\usepackage{url} % Ensure URLs are properly formatted
\usepackage{xcolor}

\pagecolor[rgb]{0.0,0.0,0.0}
\color[rgb]{1,1,1}

\usepackage[section]{placeins} % ensures that floats are placed in their section
\makeatletter
\AtBeginDocument{%
  \expandafter\renewcommand\expandafter\subsection\expandafter{%
    \expandafter\FloatBarrier\subsection
  }%
}
\makeatother

% \makeatletter
% \AtBeginDocument{%
%   \expandafter\renewcommand\expandafter\subsubsection\expandafter{%
%     \expandafter\FloatBarrier\subsubsection
%   }%
% }
% \makeatother

\usepackage{times}
\usepackage[numbers]{natbib}
\usepackage{graphicx}
\usepackage{bm} % for bold math
\usepackage{mathtools} % for \prescript
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{adjustbox}

\newcommand{\vctr}[1]{\bm{#1}}
\newcommand{\unitv}[1]{\hat{\vctr{#1}}}
\newcommand{\preup}[1]{\prescript{#1}{}{}}
\newcommand{\rf}[1]{\mathcal{\MakeUppercase{#1}}}
\newcommand{\dcm}[1]{\left[\rf{#1}\right]}
\newcommand{\vrf}[2]{\preup{\rf{#1}}\vctr{#2}}
\newcommand{\mbar}[0]{\;\middle|\;}
\newcommand{\prf}[1]{\preup{\rf{#1}}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\DeclareMathOperator{\atantwo}{atan2}
\DeclareMathOperator{\fl}{floor}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\section{Inversion Method}

@@

\begin{equation} \label{eq:nll_loss}
 f(\vctr{x}) = \frac{1}{m}\sum_{k=1}^{m}\left[\ln\sigma_k + \frac{1}{2}\left(\frac{S_k - \hat{S}_k(\vctr{x})}{\sigma_k}\right)^2 \right].
 \end{equation}

If the reflectivity of the object's faces is not well-known, we rescale the estimated light curve mean $\hat{S}(\vctr{x})$ to have equal norm to the observations to resolve the inherent albedo-area ambiguity:

\begin{equation}
  \hat{S}(\vctr{x}) = \frac{\norm{S}}{\norm{\tilde{S}(\vctr{x})}} \tilde{S}(\vctr{x}),
\end{equation}

\noindent
where $\tilde{S}(\vctr{x})$ is the original, poorly scaled, estimated light curve. In this work, the light curve and its standard deviation are always assumed to be expressed in a linear unit, e.g., analog-to-digital units (ADU) or irradiance proportional to $W/m^2$.

\subsection{State Definition and Dynamics}

@@

\subsection{Running the Solver} \ref{sec:run_solver}

Our method first initializes $n$ guesses scattered throughout the solution space -- possibly sampled from a prior distribution based on available knowledge. In the most basic case, the initial state guess is sampled for guess $i$ at iteration $k=0$:

\begin{equation}
  \vctr{x}_{0,i}(0) = \begin{bmatrix}\vctr{p}_{i,0}(0) & \vctr{\omega}_{i,0}(0) & \left(J_y / J_x\right)_{i,0} & \left(J_z / J_x\right)_{i,0}\end{bmatrix}^T.
\end{equation}

\noindent
In this work, $\vctr{p}_{i,0}(0)3$ is uniformly randomly sampled from orientation space, $\vctr{\omega}_{i,0}(0)$ is uniformly randomly sampled from the ball in $\mathbb{R}^3$ of radius $|\omega(0)|_\text{max}$ -- the maximum angular rate to search -- while $\left(J_y / J_x\right)_{i,0}$ and $\left(J_z / J_x\right)_{i,0}$ are sampled from Gaussian prior distributions centered at estimated values derived from the known geometry of the object.

After computing each initial state guess, we run the Broyden-Fletcher-Goldfarb-Shanno (BFGS) algorithm \cite{broyden1970, fletcher1970, goldfarb1970, shanno1970} to optimize each guess to a nearby local minimum $\vctr{x}_{k,i}(0)$ in the objective function such that:

\begin{equation} \label{eq:opt_problem}
  \vctr{x}_{k,i}(0) = \argmin_x f(\vctr{x}),
\end{equation}

\noindent
producing a final initial state which is a good local guess for a state which to produce the observations. In this way, we globally search the solution space up to the density implied by $n$. Using a simpler algorithm like gradient descent can still reach convergence, but will take significantly more objective function evaluations due to the high nonlinearity of the attitude inversion problem.

In order to implement this optimization effectively without constraints, it is often necessary to take the absolute value of the intermediate inertia tensor values to maintain physical validity.

\section{Computing the Light Curve}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{obs_geom.png}
  \caption{Facet geometry including the observer direction $\unitv{o}$, Sun direction $\unitv{s}$, normal vector $\unitv{n}_i$, unshadowed area $\bar{a}_i$, shadowed area $\tilde{a}_i$, and counterclockwise vertex positions $\left\{ \vctr{v}_{i,1}, \vctr{v}_{i,2}, \vctr{v}_{i,3} \right\}$.}
  \label{fig:facet_geom}
\end{figure}

In this work, the Sun position is computed using a SPICE ephemeris kernel \cite{spice} while space object positions are propagated with SGP4 TLEs obtained from Space-Track \cite{spacetrack}.

@@

Here, the scintillation noise at timestep $k$ as a function of the aperture diameter $D$ in meters, the exposure time $(\Delta t)_k$ in seconds, the zenith angle $\gamma_k$, the observing station's altitude $h_\text{obs}$ in meters, and the turbulence scaleheight $H\approx8000$ meters \cite{osborn2015}.

@@

\begin{equation} \label{eq:lc_dist}
 S_{\text{SO},k} \sim \mathcal{N}\left( \bar{S}_{\text{SO},k}, \sigma^2_{S,k} \right).
 \end{equation}

\section{Attitude Inversion Results for Synthetic Data}

\subsection{Generating the Observed Light Curve}

To demonstrate the effectiveness of our inversion method, we first present results for a simulated light curve where the ground truth is known and material property mismatch is insignificant. We produce a noisy, observed light curve for a high-fidelity scaled model of the Saturn V second stage to act as a template rocket body object, shown in Figures \ref{fig:meas_model}.

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{rocket_bodies2.png}
  \caption{Measured rocket body model \cite{nasa_models}.}
  \label{fig:meas_model}
\end{figure}

Table \ref{tb:case1_in} describes the simulated observation scenario while Table \ref{tb:synth_matprops} lists the material properties used in this test case.

\begin{table}[H]
  \centering
  \caption{Simulated observation parameters}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Target COSPAR ID & 1990-054D \\ \hline
  First obs.\ (UTC) & Mar 8, 2025 02:00:00.000 \\ \hline
  Light curve duration & $5$ minutes \\ \hline
  Observations & $100$ \\ \hline
  Integration time & $0.5$ seconds \\ \hline
  \end{tabular}
  \label{tb:case1_in}
\end{table}

\begin{table}[H]
  \centering
  \caption{Reflection properties of materials used in the synthetic data test case. The authors estimated the white paint parameters qualitatively}
  \vspace*{6pt}
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Material} & $C_d$ & $C_s$ & $n$ \\ \hline
  Aluminum \cite{fankhauser2023} & $0.34$ & $0.40$ & $8.9$ \\ \hline
  White paint & $0.9$ & $0.1$ & $1$ \\ \hline
  \end{tabular}
  \label{tb:synth_matprops}
\end{table}

The true attitude profile and inertia tensor ratios of the object are listed in Table \ref{tb:synth_att}.

\begin{table}[H]
  \centering
  \caption{True object attitude profile for all test cases}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
 Initial $\vctr{p}(0)$ & $-\frac{1}{3} \begin{bmatrix} 1 & 1 & 1 \end{bmatrix}^T$ \\ \hline
 True $\vctr{\omega}(0)$ ($\text{rad}/\text{s}$) & $\vctr{\omega}(0) = \begin{bmatrix} 0.03 & 0.06 & 0.03 \end{bmatrix}^T$ \\ \hline
 Inertia tensor ratios & $J_y / J_x = 1, \: J_z / J_x = 0.25$ \\ \hline
 External torque $\vctr{M}$ & $\begin{bmatrix} 0 & 0 & 0 \end{bmatrix}^T$ \\ \hline
  \end{tabular}
  \label{tb:synth_att}
\end{table}
\FloatBarrier

Simulating the mean light curve and its approximate probability distribution via Equation \ref{eq:lc_dist} produces the light curve displayed in ADU in Figure \ref{fig:obs_adu_synth} and V-band magnitude in Figure \ref{fig:obs_mag_synth}.

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{light_curves_adu_rocket_body.png}
  \caption{Simulated observed flux for the rocket body.}
  \label{fig:obs_adu_synth}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{light_curves_mag_rocket_body.png}
  \caption{Simulated observed V-band magnitude for the rocket body.}
  \label{fig:obs_mag_synth}
\end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=\figsmall]{light_curves_std_rocket_body.png}
%   \caption{Simulated observed light curve standard deviation computed with Equation \ref{eq:sigma_total}.}
%   \label{fig:obs_std_synth}
% \end{figure}

\subsection{Synthetic Light Curve Optimization Results}

To emulate the reality that the precise geometry of the observed object is usually uncertain, we use perform attitude inversion with a significantly simplified rocket body model, shown in Figure \ref{fig:inv_model}.

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{rocket_bodies1.png}
  \caption{Simplified rocket body model used for inversion.}
  \label{fig:inv_model}
\end{figure}

A total of $10^5$ initial state guesses were created via the sampling scheme described in Section \ref{sec:run_solver} with $|\omega(0)|_\text{max}=5.26$ degrees per second using an angular velocity padding factor of $f_\omega=1.25$. BFGS minimization was then performed for each initial guess to locally solve the optimization problem given by Equation \ref{eq:opt_problem}.

Figures \ref{fig:sigma_sols1} and \ref{fig:omega_sols1} display the converged MRP and angular velocity vectors of the best solutions TODO: define how we are determining what's best.

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{sigma_solsRocket Body.png}
  \caption{Converged solution initial orientation MRP vectors.}
  \label{fig:sigma_sols1}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{omega_sols_Rocket Body.png}
  \caption{Converged solution initial body-frame angular velocities.}
  \label{fig:omega_sols1}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{spin_proc_Rocket Body.png}
  \caption{Converged solution body-frame spin and precession rates.}
  \label{fig:spin_proc1}
\end{figure}

The inversion

\section{Attitude Inversion Results for Real Data}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figsmall]{star37e.JPG}
  \caption{Star-37E upper stage \cite{star37_af}.}
  \label{fig:star37e}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_models_002.png}
  \caption{Simplified Star-37E model used for inversion.}
  \label{fig:star37e_simple}
\end{figure}

@@

\begin{table}[H]
  \centering
  \caption{Delta I rocket body observation parameters}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Target COSPAR ID & 1984-115C \\ \hline
  First obs.\ (UTC) & Mar 2, 2025 01:53:30.251 \\ \hline
  Light curve duration & $7.5$ minutes \\ \hline
  Observations & $100$ ($92$ extracted) \\ \hline
  Obs.\ frequency & $0.222$ Hz \\ \hline
  Integration time & $3$ seconds \\ \hline
  \end{tabular}
  \label{tb:case1_in}
\end{table}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_lcs_001_2_00x.png}
  \caption{Selected light curve for the Delta (Star-37E) rocket body, observed by the Purdue Optical Ground Station}
  \label{fig:rb_lc_obs}
\end{figure}

\begin{table}[H]
  \centering
  \caption{Delta I rocket body inversion assumptions}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Uniform BRDF & $C_d=0.2$, $C_s=0.8$, $n=30$ \\ \hline
  $|\omega(0)|_\text{max}$ & $8.31$ $\text{deg} / \text{s}^{-1}$ \\ \hline
  \end{tabular}
  \label{tb:case1_ass}
\end{table}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figbig]{EchoStar-1_image.jpg}
  \caption{ECHOSTAR II artist's rendition \cite{as7000_astronautix}.}
  \label{fig:echostar1}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_models_001.png}
  \caption{Simplified ECHOSTAR II box-wing model used for inversion.}
  \label{fig:echostar1_simple}
\end{figure}

The contribution of the bus to the total inertia tensor of ECHOSTAR II is spherically symmetric and given by \cite{satterly1958}:

@@

\noindent
assuming that the center of mass (COM) of the bus coincides with the COM of the entire vehicle. By the intermediate axis theorem, the contribution of a panel to the inertia tensor is a function of the displacement of the panel's COM from the vehicle's overall COM $\vctr{r}_p = [ 0, s/2 - l_p/2, 0]^T$:

@@

\noindent
assuming that the panels have negligible thickness. The overall inertia tensor for ECHOSTAR II is therefore:

@@

\begin{table}[H]
  \centering
  \caption{ECHOSTAR II observation parameters}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Target COSPAR ID & 1996-055A \\ \hline
  First obs.\ (UTC) & Feb 26, 2025 04:16:12.279 \\ \hline
  Light curve duration & $19.5$ minutes \\ \hline
  Observations & $456$ ($395$ extracted) \\ \hline
  Obs.\ frequency & $0.388$ Hz \\ \hline
  Integration time & $1$ seconds \\ \hline
  \end{tabular}
  \label{tb:case2_in}
\end{table}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_lcs_002_2_00x.png}
  \caption{Selected light curve for ECHOSTAR II, observed by the Purdue Optical Ground Station}
  \label{fig:sat_lc_obs}
\end{figure}

We estimate a maximum bound for the angular velocity magnitude by taking the Fourier transform of the light curve and choosing the highest-power positive frequency, converting to radians per second and multiplying by a factor of safety $f_\omega > 1$. TODO: mention this factor in an equation.

\begin{table}[H]
  \centering
  \caption{ECHOSTAR II inversion assumptions}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Material} & \textbf{Coefficients} \\ \hline
  Aluminum BRDF & $C_d=0.22$, $C_s=0.4$, $n=5$ \\ \hline
  MLI BRDF & $C_d=0.05$, $C_s=0.24$, $n=20$ \\ \hline
  Solar panel BRDF & $C_d=0.05$, $C_s=0.13$, $n=10$ \\ \hline
  $|\omega(0)|_\text{max}$ & $2.32$ $\text{deg} / \text{s}^{-1}$ \\ \hline
  \end{tabular}
  \label{tb:case2_ass}
\end{table}

\section*{Acknowledgments}

@@

\section*{Appendix}

\begin{table}[H]
  \centering
  \caption{Telescope information common to all test cases}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  CCD sensor & KAF-16803 \\ \hline
  Effective aperture area $A_\circ$ & $0.076$ $m^2$ \\ \hline
  Observer location & $32.900^\circ \textrm{ N}, -105.533^\circ \textrm{ W}$ \\ \hline
  Observer altitude & $2.24$ km above MSL \\ \hline
  Source pixels $n_\text{pix}$ & $100$ \\ \hline
  Read noise $\sigma_\text{read}$ & $9$ $\text{ADU} / \text{pixel}$ \\ \hline
  Dark current rate $\lambda_\text{dark}$ & $0.01$ $\text{ADU} / \text{pixel} / \text{s}$ \\ \hline
  Flat field strength $f_k$ & $0.01$ nondim \\ \hline
  Gain $g$ & $5.1$ $e^- / \text{ADU}$ \\ \hline
  \end{tabular}
  \label{tb:tele_info}
 \end{table}

 \begin{table}[H]
  \centering
  \caption{BFGS solver configuration for all results cases}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  Maximum function evaluations & $1000$ \\ \hline
  Maximum iterations & $100$ \\ \hline
  Finite difference step size & $1 \cdot 10^{-5}$ \\ \hline
  Gradient $\infty$-norm tolerance & $1 \cdot 10^{-5}$ \\ \hline
  \end{tabular}
  \label{tb:bfgs_info}
 \end{table}

\bibliography{cache/refs.bib}
\end{document}
